---
title: "Literature_Rev_2023"
author: "Ken Suzuki"
date: "2023-09-02"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyverse)
library(gt)
library(gtsummary)
library(webshot2)

# Read excel file
master_dat <- read_excel("~/Desktop/IRP/Literature_review_2023/raw_data/Dat_01.xlsx")
```


#### 1) Mean Score by Study
```{r, echo=FALSE} 
# Get Row Means and Column Means.
study_mean <- master_dat %>%
  slice(4:n()) %>%
  select(-c(1, 3))

# Replace "YES" with 1 and "NO" with 0 in columns Q01 to Q47
study_mean <- study_mean %>%
  mutate(across(Q01:Q47, ~ case_when(
    . == "Yes" ~ as.numeric(1),
    . == "No" ~ as.numeric(0),
    is.na(.) ~ NA_real_
  )))

study_mean <- study_mean %>% 
  mutate(across(starts_with("Q"), as.numeric))

# Calculate row means for columns Q01 to Q47, rounded to 3 decimal places
study_mean <- study_mean %>%
  rowwise() %>%
  mutate(Mean = round(mean(c_across(Q01:Q47), na.rm = TRUE), 3)) %>%
  ungroup()

# Create tables
study_table <- master_dat %>%
  left_join(study_mean, by = "ID") %>%
  select(ID, Study, Author, Mean) 

# Remove first three rows from study_table
study_table <- study_table %>%
  slice(4:n())

# Create gt table and change the font size
gt_table <- gt(study_table) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )

# Display the gt table
gt_table

# Save table as .png image
gt::gtsave(gt_table, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_table.png")
```

#### 2) Mean Scores by Criterion
```{r, echo=FALSE}
# Calculate column means 
question_mean <- study_mean %>%
  select(-ID) %>%  # Remove ID column
  summarise(across(everything(), \(x) round(mean(x, na.rm = TRUE), 3)))

# Extract the third row and transpose it
question_table <- master_dat %>% 
  slice(3) %>%
  gather(key = "variable", value = "value", -ID) 

# Remove the first two rows and the first column from the transposed dataset
question_table <- question_table %>%
  slice(-(1:2)) %>%
  select(-ID)   

# Extract the first row and transpose it
V1 <- master_dat %>% 
  slice(1) %>%
  gather(key = "variable", value = "value", -ID) 

# Remove the first two rows and the first column from the transposed dataset
V1 <- V1 %>%
  slice(-(1:2)) %>%
  select(-ID)   

# Extract the first row and transpose it
V2 <- master_dat %>% 
  slice(2) %>%
  gather(key = "variable", value = "value", -ID) 

# Remove the first two rows and the first column from the transposed dataset
V2 <- V2 %>%
  slice(-(1:2)) %>%
  select(-ID)   

# Combine value columns of V1 and V2 into question_table
question_table <- question_table %>%
  left_join(V1, by = "variable") %>%
  left_join(V2, by = "variable")

# Transpose question_mean and convert it into a data frame suitable for joining
question_mean <- question_mean %>%
  gather(key = "variable", value = "Mean")

# Add question_mean values as the new variable "Mean"
question_table <- question_table %>%
  left_join(question_mean, by = "variable")

# Add question_mean values as the new variable "Mean"
question_mean <- question_mean %>%
  gather(key = "variable", value = "Mean") %>%
  mutate(Mean = round(Mean, 2))
  
# Rename variables
question_table <- question_table %>% 
  rename(ID = variable,
         Question = value.x,
         Section = value.y,
         Topic = value)

# Change the order of appearance
question_table <- question_table %>% 
  select(ID, Section, Topic, Question, Mean)

# Create gt table and change the font size
gt_question_table <- gt(question_table) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )
gt_question_table

# Save table as .png image
gt::gtsave(gt_question_table, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_question_table.png")
```


#### 3) Mean Scores by Section 
```{r, echo=FALSE}

# Set the factor levels for the Section column in custom order
question_table$Section <- factor(question_table$Section, 
                                 levels = c("Abstract", "Introduction", "Methods", "Results", "Discussion"))

# Compute the mean by section
section_table <- question_table %>%
  group_by(Section) %>%
  summarise(Mean = mean(Mean, na.rm = TRUE)) %>%
  mutate(Mean = round(Mean, 3)) 

# Create gt table and change the font size
gt_section_table <- gt(section_table) %>%
  tab_options(
    table.font.size = px(15)
  ) %>% 
  cols_align(
    align = "left"
  )

gt_section_table
gt::gtsave(gt_section_table, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_section_table.png")
```

#### 4) Mean Scores by Topic
```{r, echo=FALSE}
# Assuming question_table is defined and appropriate libraries are loaded
topic_table <- question_table %>%
  group_by(Topic, Section) %>%
  summarise(Mean = mean(Mean, na.rm = TRUE), .groups = 'drop') %>%
  mutate(Mean = round(Mean, 3))

# Create gt table and change the font size
gt_topic_table <- gt(topic_table) %>%
  tab_options(table.font.size = px(15)) %>%
  cols_align(
    align = "left",
    columns = c(Topic, Section, Mean)
  )  # Closing parenthesis was missing here

# Print the table
gt_topic_table

# Save table as .png image
gt::gtsave(gt_topic_table, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_topic_table.png")

```

#### 4) Machine Learning Models by Category
```{r, echo = FALSE}

# Create the data frame
df <- data.frame(
  Category = c(
    "Regression-based models", "Support Vector Machines", "Decision Trees and Ensembles",
    "Neural Networks", "Bayesian Models", "Instance-based models", "Other"
  ),
  Frequency = c(7, 13, 17, 4, 17, 5, 18)
)

# Sort by frequency, but place 'Other' at the bottom
df_sorted <- df[df$Category != "Other", ]
df_sorted <- df_sorted[order(-df_sorted$Frequency), ]
df_other <- df[df$Category == "Other", ]
df_final <- rbind(df_sorted, df_other)

gt_Category <- gt(df_final) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )
gt_Category


# Save table as .png image
gt::gtsave(gt_Category, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_Category.png")
```

#### 5) ML Category Breakdown

##### Regression based model
```{r, echo=FALSE}

regression_based_models <- data.frame(
  Regression = c("LASSO", "Elastic Net", "Logistic Regression", "Linear Regression", "Multiple Linear Regression", "Non-linear Regression"),
  Frequency = c(2, 2, 2, 1, 1, 1)
)
# Create gt table for regression_based_models and adjust the font size
gt_regression_based_models <- gt(regression_based_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_regression_based_models

# Save table as .png image
gt::gtsave(gt_regression_based_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_regression_based_models.png")
```

##### SVM models
```{r, echo=FALSE}
svm_models <- data.frame(
  SVM = c("SVMs","SMO/kernel", "SMO"),
  Frequency = c(9, 3, 1)
)

# Create gt table for svm_models and adjust the font size
gt_svm_models <- gt(svm_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_svm_models
# Save table as .png image
gt::gtsave(gt_svm_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_svm_models.png")
```

##### Decesion Tree Ensemble Models
```{r, echo = FALSE}
decision_tree_ensemble_models <- data.frame(
  Decision_Tree = c("Random Forest", "Gradient Boosting", "XGBoost", "ADTree", "Decision Table", "J48", "LADTree", "LMT", "NBTree", "PART", "Random Tree", "REPTree", "SimpleCart"),
  Frequency = c(6, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)
)

# Create gt table for decision_tree_ensemble_models and adjust the font size
gt_decision_tree_ensemble_models <- gt(decision_tree_ensemble_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_decision_tree_ensemble_models

# Save table as .png image
gt::gtsave(gt_decision_tree_ensemble_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_decision_tree_ensemble_models.png")
```

##### Neural Network Models
```{r, echo = FALSE}
neural_network_models <- data.frame(
  Neural_Network = c("Convolutional Neural Network", "Neural Network", "Deep Neural Network", "Recurrent Neural Networks"),
  Frequency = c(1, 1, 1, 1)
)

# Create gt table for neural_network_models and adjust the font size
gt_neural_network_models <- gt(neural_network_models) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_neural_network_models

# Save table as .png image
gt::gtsave(gt_neural_network_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_neural_network_models.png")
```

##### Bayesian Models
```{r, echo = FALSE}
bayesian_models <- data.frame(
  Bayesian = c("BayesNet", "BayesNet/searchAlgorithm", "BayesNet/estimator", "Naïve Bayes"),
  Frequency = c(7, 5, 2, 1)
)

# Create gt table for bayesian_models and adjust the font size
gt_bayesian_models <- gt(bayesian_models) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_bayesian_models

# Save table as .png image
gt::gtsave(gt_bayesian_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_bayesian_models.png")
```
 
##### Instance based Models
```{r, echo = FALSE}
instance_based_models <- data.frame(
  Instance_Based = c( "Instance-Based k", "k-Nearest Neighbors (KNN)"),
  Frequency = c(4, 1)
)

# Create gt table for instance_based_models and adjust the font size
gt_instance_based_models <- gt(instance_based_models) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_instance_based_models

# Save table as .png image
gt::gtsave(gt_instance_based_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_instance_based_models.png")
```

##### Other Models
```{r, echo=FALSE}
other_models <- data.frame(
  Others = c("ADAboost Regressor", "Conjunctive Clause Evolutionary Algorithm (CCEA)", "MondoBrain Augmented Intelligence System", "Mixture models", "BFtree", "Conjunctive Rule", "DTNB", "FT", "FURIA", "KStar", "LWL", "NNGE", "RIDOR", "RBFNetwork", "SPEGASOS", "Ensemble Strategies", "Personalized Bayesian", "Hidden Markov"),
  Frequency = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1,1,1)
)

# Create gt table for other_models and adjust the font size
gt_other_models <- gt(other_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_other_models

# Save table as .png image
gt::gtsave(gt_other_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_other_models.png")
```

#### 5) List of Top Performers

```{r, echo=FALSE}
# Define the custom order for the 'Section' column
ordered_sections <- c("Abstract", "Introduction", "Methods", "Results", "Discussion")

# Convert 'Section' into an ordered factor
question_top <- question_table %>%
  mutate(Section = factor(Section, levels = ordered_sections, ordered = TRUE)) %>%
  arrange(Section, desc(Topic), desc(Mean)) %>%
  filter(Mean > 0.8)

# Create gt table for question_top and adjust the font size
gt_question_top <- gt(question_top) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_question_top 

# Save table as .png image
gt::gtsave(gt_question_top, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_question_top.png")

```

# List of Bottom Performers
```{r, echo=FALSE}

# Define the custom order for the 'Section' column
ordered_sections <- c("Abstract", "Introduction", "Methods", "Results", "Discussion")

# Convert 'Section' into an ordered factor and filter for "Methods" and "Discussion"
question_bottom <- question_table %>%
  mutate(Section = factor(Section, levels = ordered_sections, ordered = TRUE)) %>%
  filter(Section %in% c("Methods", "Discussion"), Mean < 0.7) %>%
  arrange(ID, Section, desc(Mean)) %>%
  select(ID, Section, Topic, Question, Mean)

# Create gt table for question_bottom and adjust the font size
gt_question_bottom <- gt(question_bottom) %>%
  tab_options(
    table.font.size = px(15)
  )

# Display the gt table
gt_question_bottom

# Save table as .png image
gt::gtsave(gt_question_bottom, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_question_bottom.png")

```
```{r, echo=FALSE}
mean(study_mean$Mean)
min(study_mean$Mean)
max(study_mean$Mean)
```

```{r}
# Open the graphics device
png("/Users/kensuzuki/desktop/IRP/Literature_review_2023/images/histogram.png")

# Plot the histogram
hist(study_mean$Mean, 
     main = "Mean Score Distribution of 20 Studies", 
     xlab = "Mean Value", 
     col = "steelblue", 
     border = "white")

# Close the graphics device
dev.off()
```


<style>
  .gt_table {
    margin-left: 0 !important;
  }
</style>


