---
title: "Literature_Rev_2023"
author: "Ken Suzuki"
date: "2023-09-02"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyverse)
library(gt)
library(gtsummary)
library(webshot2)

# Read excel file
master_dat <- read_excel("~/Desktop/IRP/Literature_review_2023/raw_data/Dat_01.xlsx")
```


#### 1) Mean Score by Study
```{r, echo=FALSE} 
# Get Row Means and Column Means.
study_mean <- master_dat %>%
  slice(4:n()) %>%
  select(-c(1, 3))

# Replace "YES" with 1 and "NO" with 0 in columns Q01 to Q47
study_mean <- study_mean %>%
  mutate(across(Q01:Q47, ~ case_when(
    . == "Yes" ~ as.numeric(1),
    . == "No" ~ as.numeric(0),
    is.na(.) ~ NA_real_
  )))

study_mean <- study_mean %>% 
  mutate(across(starts_with("Q"), as.numeric))

# Calculate row means for columns Q01 to Q47, rounded to 3 decimal places
study_mean <- study_mean %>%
  rowwise() %>%
  mutate(Mean = round(mean(c_across(Q01:Q47), na.rm = TRUE), 3)) %>%
  ungroup()

# Create tables
study_table <- master_dat %>%
  left_join(study_mean, by = "ID") %>%
  select(ID, Study, Author, Mean) 

# Remove first three rows from study_table
study_table <- study_table %>%
  slice(4:n())

# Create gt table and change the font size
gt_table <- gt(study_table) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )

# Display the gt table
gt_table

# Save table as .png image
gt::gtsave(gt_table, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_table.png")
```

#### 2) Mean Scores by Criterion
```{r, echo=FALSE}
# Calculate column means 
question_mean <- study_mean %>%
  select(-ID) %>%  # Remove ID column
  summarise(across(everything(), \(x) round(mean(x, na.rm = TRUE), 3)))

# Extract the third row and transpose it
question_table <- master_dat %>% 
  slice(3) %>%
  gather(key = "variable", value = "value", -ID) 

# Remove the first two rows and the first column from the transposed dataset
question_table <- question_table %>%
  slice(-(1:2)) %>%
  select(-ID)   

# Extract the first row and transpose it
V1 <- master_dat %>% 
  slice(1) %>%
  gather(key = "variable", value = "value", -ID) 

# Remove the first two rows and the first column from the transposed dataset
V1 <- V1 %>%
  slice(-(1:2)) %>%
  select(-ID)   

# Extract the first row and transpose it
V2 <- master_dat %>% 
  slice(2) %>%
  gather(key = "variable", value = "value", -ID) 

# Remove the first two rows and the first column from the transposed dataset
V2 <- V2 %>%
  slice(-(1:2)) %>%
  select(-ID)   

# Combine value columns of V1 and V2 into question_table
question_table <- question_table %>%
  left_join(V1, by = "variable") %>%
  left_join(V2, by = "variable")

# Transpose question_mean and convert it into a data frame suitable for joining
question_mean <- question_mean %>%
  gather(key = "variable", value = "Mean")

# Add question_mean values as the new variable "Mean"
question_table <- question_table %>%
  left_join(question_mean, by = "variable")

# Add question_mean values as the new variable "Mean"
question_mean <- question_mean %>%
  gather(key = "variable", value = "Mean") %>%
  mutate(Mean = round(Mean, 2))
  
# Rename variables
question_table <- question_table %>% 
  rename(ID = variable,
         Question = value.x,
         Section = value.y,
         Topic = value)

# Change the order of appearance
question_table <- question_table %>% 
  select(ID, Section, Topic, Question, Mean)

# Create gt table and change the font size
gt_question_table <- gt(question_table) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )
gt_question_table

# Save table as .png image
gt::gtsave(gt_question_table, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_question_table.png")
```


#### 3) Mean Scores by Section 
```{r, echo=FALSE}

# Set the factor levels for the Section column in custom order
question_table$Section <- factor(question_table$Section, 
                                 levels = c("Abstract", "Introduction", "Methods", "Results", "Discussion"))

# Compute the mean by section
section_table <- question_table %>%
  group_by(Section) %>%
  summarise(Mean = mean(Mean, na.rm = TRUE)) %>%
  mutate(Mean = round(Mean, 3)) 

# Create gt table and change the font size
gt_section_table <- gt(section_table) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )
gt_section_table

```

#### 4) Mean Scores by Topic
```{r, echo=FALSE}
# Compute the mean by Topic
topic_table <- question_table %>%
  group_by(Topic) %>%
  summarise(Mean = mean(Mean, na.rm = TRUE)) %>%
  mutate(Mean = round(Mean, 3)) 



# Create gt table and change the font size
gt_topic_table <- gt(topic_table) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )
gt_topic_table

# Save table as .png image
gt::gtsave(gt_topic_table, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_topic_table.png")
```

#### 4) Machine Learning Models by Category
```{r, echo = FALSE}

# Create the data frame
df <- data.frame(
  Category = c(
    "Regression-based models", "Support Vector Machines", "Decision Trees and Ensembles",
    "Neural Networks", "Bayesian Models", "Instance-based models", "Boosting Algorithms",
    "Hidden Markov Models", "Other"
  ),
  Frequency = c(7, 13, 17, 4, 17, 5, 1, 1, 22)
)

# Sort by frequency, but place 'Other' at the bottom
df_sorted <- df[df$Category != "Other", ]
df_sorted <- df_sorted[order(-df_sorted$Frequency), ]
df_other <- df[df$Category == "Other", ]
df_final <- rbind(df_sorted, df_other)

gt_Category <- gt(df_final) %>%
  tab_options(
    table.font.size = px(15)  # Adjust the font size here
  )
gt_Category


# Save table as .png image
gt::gtsave(gt_Category, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_Category.png")
```

#### 5) ML Category Breakdown

##### Regression based model
```{r, echo=FALSE}

regression_based_models <- data.frame(
  Regression = c("LASSO", "Elastic Net", "Linear Regression", "Multiple Linear Regression", "Non-linear Regression"),
  Frequency = c(2, 2, 1, 1, 1)
)
# Create gt table for regression_based_models and adjust the font size
gt_regression_based_models <- gt(regression_based_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_regression_based_models

# Save table as .png image
gt::gtsave(gt_regression_based_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_regression_based_models.png")
```

##### SVM models
```{r, echo=FALSE}
svm_models <- data.frame(
  SVM = c("SVMs","SMO/kernel", "SMO"),
  Frequency = c(9, 3, 1)
)

# Create gt table for svm_models and adjust the font size
gt_svm_models <- gt(svm_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_svm_models
# Save table as .png image
gt::gtsave(gt_svm_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_svm_models.png")
```

##### Decesion Tree Ensemble Models
```{r, echo = FALSE}
decision_tree_ensemble_models <- data.frame(
  Decision_Tree = c("Random Forest", "Gradient Boosting", "XGBoost", "ADTree", "Decision Table", "J48", "LADTree", "LMT", "NBTree", "PART", "Random Tree", "REPTree", "SimpleCart"),
  Frequency = c(6, 2, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)
)

# Create gt table for decision_tree_ensemble_models and adjust the font size
gt_decision_tree_ensemble_models <- gt(decision_tree_ensemble_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_decision_tree_ensemble_models

# Save table as .png image
gt::gtsave(gt_decision_tree_ensemble_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_decision_tree_ensemble_models.png")
```

##### Neural Network Models
```{r, echo = FALSE}
neural_network_models <- data.frame(
  Neural_Network = c("Convolutional Neural Network", "Neural Network", "Deep Neural Network", "Recurrent Neural Networks"),
  Frequency = c(1, 1, 1, 1)
)

# Create gt table for neural_network_models and adjust the font size
gt_neural_network_models <- gt(neural_network_models) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_neural_network_models

# Save table as .png image
gt::gtsave(gt_neural_network_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_neural_network_models.png")
```

##### Bayesian Models
```{r, echo = FALSE}
bayesian_models <- data.frame(
  Bayesian = c("BayesNet", "BayesNet/searchAlgorithm", "Logistic Regression", "BayesNet/estimator", "Naïve Bayes"),
  Frequency = c(7, 5, 2, 2, 1)
)

# Create gt table for bayesian_models and adjust the font size
gt_bayesian_models <- gt(bayesian_models) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_bayesian_models

# Save table as .png image
gt::gtsave(gt_bayesian_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_bayesian_models.png")
```
 
##### Instance based Models
```{r, echo = FALSE}
instance_based_models <- data.frame(
  Instance_Based = c( "IBk/nNSearchAlgorithm", "K-nearest neighbors (KNN)", "IBk"),
  Frequency = c(3, 1, 1)
)

# Create gt table for instance_based_models and adjust the font size
gt_instance_based_models <- gt(instance_based_models) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_instance_based_models

# Save table as .png image
gt::gtsave(gt_instance_based_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_instance_based_models.png")
```

##### Boosting Algorithms
```{r, echo=FALSE}
boosting_algorithms <- data.frame(
  Boosting_Algorithms = c("ADAboost Regressor"),
  Frequency = c(1)
)

# Create gt table for boosting_algorithms and adjust the font size
gt_boosting_algorithms <- gt(boosting_algorithms) %>%
  tab_options(
    table.font.size = px(15)
  )

gt_boosting_algorithms

# Save table as .png image
gt::gtsave(gt_boosting_algorithms, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_boosting_algorithms.png")
```

##### Hidden Markov Models
```{r, echo=FALSE}
hidden_markov_models <- data.frame(
  Hidden_Markov = c("Hidden Markov"),
  Frequency = c(1)
)

# Create gt table for hidden_markov_models and adjust the font size
gt_hidden_markov_models <- gt(hidden_markov_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_hidden_markov_models


# Save table as .png image
gt::gtsave(gt_hidden_markov_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_hidden_markov_models.png")
```

##### Other Models
```{r, echo=FALSE}
other_models <- data.frame(
  Others = c("Conjunctive Clause Evolutionary Algorithm (CCEA)", "MondoBrain Augmented Intelligence System", "Mixture models", "BFtree", "Conjunctive Rule", "DTNB", "FT", "FURIA", "KStar", "LWL", "NNGE", "RIDOR", "RBFNetwork", "SPEGASOS", "Ensemble Strategies", "Personalized Bayesian"),
  Frequency = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1)
)

# Create gt table for other_models and adjust the font size
gt_other_models <- gt(other_models) %>%
  tab_options(
    table.font.size = px(15)
  )
gt_other_models

# Save table as .png image
gt::gtsave(gt_other_models, filename = "/Users/kensuzuki/Desktop/IRP/Literature_review_2023/Images/gt_other_models.png")
```


<style>
  .gt_table {
    margin-left: 0 !important;
  }
</style>


